On the discretization of Laplace's equation with Neumann boundary conditions on polygonal domains

### 2020-01-15 paper_lap/01intro.tex
updting paper

 Finally, a recent approach is based on leveraging explicit representations of the solutions to the BIEs in the vicinity of the corner as sums of fractional powers depending on the angle \cite{serkhacha}. Using these representations one can construct high-order discretizations which introduce relatively few extra degrees of freedom near the corners (i.e. an amount which is comparable to the number required for smooth portions of the boundary). This approach has been used to generate efficient discretizations for Dirichlet problems for Laplace's equation on polygonal domains\cite{hoskins2019numerical}.

>>>>

 Finally, a recent approach is based on leveraging explicit representations of the solutions to the BIEs in the vicinity of the corner as sums of fractional powers depending on the angle \cite{serkhacha,serkh2016solution}. Using these representations one can construct high-order discretizations which introduce relatively few extra degrees of freedom near the corners (i.e. an amount which is comparable to the number required for smooth portions of the boundary). This approach has been used to generate efficient discretizations for Dirichlet problems for Laplace's equation on polygonal domains\cite{hoskins2019numerical}.

### 2020-01-15 paper_lap/06num.tex
updting paper

\section{Numerical results \label{sec:num}}
\subsection{Accuracy}
In this section, we demonstrate the accuracy of the proposed numerical method (both in the {\it weak} sense 
described above, 
as well as in the classical sense after sufficiently many re-solves) on the triangular domain shown below. 
The reference solution for each of the examples is computed using a discretization with
a graded mesh in the vicinity of the corners, where the smallest panel at the corner is $2^{-150}$ times
the length of the first macroscopic panel away from the corner (see~\cref{fig:dom}). In these examples, the solutions are computed via dense linear solves.

\begin{figure}
\begin{center}
\includegraphics[width=0.7\linewidth]{media/discretization}
\caption{Problem domain and panel discretization of the boundary. The discretization on the left is based on using the Dirichlet
discretization at corner panels (indicated by blue panels) discussed in~\cref{sec:disc_dir}, while the discretization on the right is a sample discretization with 2 levels of refinement in the vicinity of the corner. All the panels in black are discretized using scaled Gauss-Legendre nodes. The square ticks indicate location of the charges $\bx_{j}$ for defining the boundary data for the scattering problem.}
\label{fig:dom}
\end{center}
\end{figure}

\begin{rem}
Though $2^{-150}$ is significantly smaller than machine precision, the matrix entries corresponding to the
corner interactions can be computed accurately by translating the corners to the origin when 
computing interactions of nearby points.
\end{rem} 
\begin{rem}
Simple arguments from complex analysis show that when using graded meshes, in order to obtain full 
machine precision 
($\sim 1.11 \times 10^{-16}$) for solutions of the Neumann problem at any point in the interior 
at least $10^{-16}$ away from a corner, it suffices to choose the smallest panel (i.e. the size of the 
panel closest to the corner) to be of size $2^{-100}.$ However, resulting values of the density will not be 
accurate to machine precision at all nodes. In fact the quality
of the density deteriorates as one approaches the corner. Thus, in order to obtain accurate point values
of the density to machine precision at all points which are at least $2^{-100}$ away from the corner, we use a smallest
panel size of $2^{-150}$. 
\end{rem}

The potential at target locations which are sufficiently far from the boundary (i.e. at least one panel length away from 
every panel) is the inner product of the 
density with a smooth function and hence can be computed accurately without re-solving (see~\cref{rem:far-field-accuracy}). For a target 
location $\boldsymbol{y}$, we compute the potential via the formula,
\begin{equation}
\label{eq:farfieldpot}
u(\by) = \int_{\Gamma} G(\bx,\by) \sigma(\bx) dS_{\bx} \approx \sum_{i=1}^{N}  G(\gamma(s_{i}),\by) \sigma_{i} \sqrt{w_{i}}
\end{equation}
In~\cref{fig:scatteringtest}, we compute the error in the solution at target
locations for a scattering problem whose right hand side is given by a collection of three interior charges
\begin{equation}
\label{eq:scatboundarydata}
f(\bx) = -\nabla  \left(\sum_{j=1}^{3} \log |\bx - \bx_{j}|  \right)  \cdot \bnu(\bx)\, ,  
\end{equation}
where the locations $\bx_{j}$ are denoted by square dots in~\cref{fig:scatteringtest}. Note that the density $\sigma$ plotted
as a function of arclength goes to infinity at the corner vertices, indicating that the native Dirichlet discretization 
presented in~\cref{sec:disc_dir} wouldn't have sufficed. However, the potential in the volume is accurate to 14 digits at
target locations away from the boundary. 
\begin{figure}
\begin{center}
\includegraphics[width=\linewidth]{media/weaktest}
\caption{Left panel: Solution to Neumann problem with data given by~\cref{eq:scatboundarydata}, center panel: error in computing the potential in the formula using the underlying smooth quadrature~\cref{eq:farfieldpot}, and on the right the density $\sigma$ as a function of arc-length}.
\label{fig:scatteringtest}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\linewidth]{media/density}
\caption{Top row: (left) Illustrative mesh used for iteratively computing the solution in the vicinity of a corner, (right) the density in the vicinity of one of the corner panels. Bottom row: error in computing the density, where $\tilde{\sigma}$ denotes the density computed using special purpose discretizations at corner panels, and $\tilde{\sigma_{g}}$ denotes the density using a graded mesh with the smallest panel equal to the length of the smallest panel after the iterative resolve procedure. The errors are scaled by square roots of the quadrature weights.    }.
\label{fig:dens-error}
\end{center}
\end{figure}

After re-solving the density, the solution is evaluated on a tensor product polar grid, where the grid
is exponentially spaced in the radial direction and equispaced in the angular direction. For evaluation points (targets)
close to panels which are not at the corner, we use adaptive integration in order to resolve the near-singular behavior of
the kernel for accurate computation of the integrals. For target locations close to the corner panel, since we do not have
the capability to interpolate the density, we use the underlying smooth quadrature rules for computing their contribution. 
The reference solution and the errors are demonstrated in~\cref{fig:vol-plot}.
\begin{figure}
\begin{center}
\includegraphics[width=\linewidth]{media/volume}
\caption{Top row: Solution on the volume after 10, 20, and 40 iterations of re-solve. The solution is computed on a tensor product polar grid, where the evaluation points (targets) are exponentially spaced in the radial direction. The closest target location is approximately $10^{-13}$ away from the corner. Near quadrature is handled via adaptive integration except for the corner panel where the smooth quadrature weights are used. Bottom row: analogous results where the solution is computed using a graded mesh.   }.
\label{fig:vol-plot}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\linewidth]{media/magnetron}
\caption{(left): Boundary data as a function of arclength, (center): absolute value of density as a function of arclength, and 
(right): $\log_{10}$ of the absolute value of the solution in the volume computed using an FMM.}
\label{fig:magnetron}
\end{center}
\end{figure}

>>>>

\section{Numerical results \label{sec:num}}
\subsection{Accuracy}
In this section, we demonstrate the accuracy of the proposed numerical method (both in the {\it weak} sense 
described above, 
as well as in the classical sense after sufficiently many re-solves) on the triangular domain shown below. 
The reference solution for each of the examples is computed using a discretization with
a graded mesh in the vicinity of the corners, where the smallest panel at the corner is $2^{-200}$ times
the length of the first macroscopic panel away from the corner (see~\cref{fig:dom}). In these examples, the solutions are computed via dense linear solves.

\begin{figure}
\begin{center}
\includegraphics[width=0.7\linewidth]{paper-figs/discretization}
\caption{Problem domain and panel discretization of the boundary. The discretization on the left is based on using the Dirichlet
discretization at corner panels (indicated by blue panels) discussed in~\cref{sec:disc_dir}, while the discretization on the right is a sample discretization with 2 levels of refinement in the vicinity of the corner. All the panels in black are discretized using scaled Gauss-Legendre nodes. The square ticks indicate location of the charges $\bx_{j}$ for defining the boundary data for the scattering problem.}
\label{fig:dom}
\end{center}
\end{figure}

\begin{rem}
Though $2^{-200}$ is significantly smaller than machine precision, the matrix entries corresponding to the
corner interactions can be computed accurately by translating the corners to the origin when 
computing interactions of nearby points.
\end{rem} 
\begin{rem}
Simple arguments from complex analysis show that when using graded meshes, in order to obtain full 
machine precision 
($\sim 1.11 \times 10^{-16}$) for solutions of the Neumann problem at any point in the interior 
at least $10^{-16}$ away from a corner, it suffices to choose the smallest panel (i.e. the size of the 
panel closest to the corner) to be of size $2^{-100}.$ However, resulting values of the density will not be 
accurate to machine precision at all nodes. In fact the quality
of the density deteriorates as one approaches the corner. Thus, in order to obtain accurate point values
of the density to machine precision at all points which are at least $2^{-100}$ away from the corner, we use a smallest
panel size of $2^{-200}$. 
\end{rem}

The potential at target locations which are sufficiently far from the boundary (i.e. at least one panel length away from 
every panel) is the inner product of the 
density with a smooth function and hence can be computed accurately without re-solving (see~\cref{rem:far-field-accuracy}). For a target 
location $\boldsymbol{y}$, we compute the potential via the formula,
\begin{equation}
\label{eq:farfieldpot}
u(\by) = \int_{\Gamma} G(\bx,\by) \sigma(\bx) dS_{\bx} \approx \sum_{i=1}^{N}  G(\gamma(s_{i}),\by) \sigma_{i} \sqrt{w_{i}}
\end{equation}
In~\cref{fig:scatteringtest}, we compute the error in the solution at target
locations for a scattering problem whose right hand side is given by a collection of three interior charges
\begin{equation}
\label{eq:scatboundarydata}
f(\bx) = -\nabla  \left(\sum_{j=1}^{3} \log |\bx - \bx_{j}|  \right)  \cdot \bnu(\bx)\, ,  
\end{equation}
where the locations $\bx_{j}$ are denoted by square dots in~\cref{fig:scatteringtest}. Note that the density $\sigma$ plotted
as a function of arclength goes to infinity at the corner vertices, indicating that the native Dirichlet discretization 
presented in~\cref{sec:disc_dir} wouldn't have sufficed. However, the potential in the volume is accurate to 14 digits at
target locations away from the boundary. 
\begin{figure}
\begin{center}
\includegraphics[width=\linewidth]{paper-figs/weaktest}
\caption{Left panel: Solution to Neumann problem with data given by~\cref{eq:scatboundarydata}, center panel: error in computing the potential in the formula using the underlying smooth quadrature~\cref{eq:farfieldpot}, and on the right the density $\sigma$ as a function of arc-length}.
\label{fig:scatteringtest}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\linewidth]{paper-figs/density}
\caption{Top row: (left) Illustrative mesh used for iteratively computing the solution in the vicinity of a corner, (right) the density in the vicinity of one of the corner panels. Bottom row: error in computing the density, where $\tilde{\sigma}$ denotes the density computed using special purpose discretizations at corner panels, and $\tilde{\sigma_{g}}$ denotes the density using a graded mesh with the smallest panel equal to the length of the smallest panel after the iterative resolve procedure. The errors are scaled by square roots of the quadrature weights.    }.
\label{fig:dens-error}
\end{center}
\end{figure}

After re-solving the density, the solution is evaluated on a tensor product polar grid, where the grid
is exponentially spaced in the radial direction and equispaced in the angular direction. For evaluation points (targets)
close to panels which are not at the corner, we use adaptive integration in order to resolve the near-singular behavior of
the kernel for accurate computation of the integrals. For target locations close to the corner panel, since we do not have
the capability to interpolate the density, we use the underlying smooth quadrature rules for computing their contribution. 
The reference solution and the errors are demonstrated in~\cref{fig:vol-plot}.
\begin{figure}
\begin{center}
\includegraphics[width=\linewidth]{paper-figs/volume}
\caption{Top row: Solution on the volume after 10, 20, and 40 iterations of re-solve. The solution is computed on a tensor product polar grid, where the evaluation points (targets) are exponentially spaced in the radial direction. The closest target location is approximately $10^{-13}$ away from the corner. Near quadrature is handled via adaptive integration except for the corner panel where the smooth quadrature weights are used. Bottom row: analogous results where the solution is computed using a graded mesh.   }.
\label{fig:vol-plot}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\linewidth]{paper-figs/magnetron}
\caption{(left): Boundary data as a function of arclength, (center): absolute value of density as a function of arclength, and 
(right): $\log_{10}$ of the absolute value of the solution in the volume computed using an FMM.}
\label{fig:magnetron}
\end{center}
\end{figure}

### 2020-01-15 paper_lap/07conc.tex
updting paper

Though the present paper treats only Laplace's equation for polygonal domains, the method shown here extends 
much more broadly. In particular, the approach easily extends to accommodate curved boundaries. Moreover, in addition 
to Laplace's equation, this approach can be easily adapted to solve the Helmholtz equation and the biharmonic equation with analogous boundary conditions. A manuscript detailing this extension is currently in preparation.

>>>>

Though the present paper treats only Laplace's equation for polygonal domains, the method shown here extends 
much more broadly. In particular, the approach easily extends to accommodate curved boundaries. Moreover, in addition 
to Laplace's equation, this approach can be easily adapted to solve the Helmholtz equation and the biharmonic equation with analogous boundary conditions for which the nature of singularities of corresponding integral equations have been analyzed~\cite{serkhrachh,serkhpnas}. A manuscript detailing this extension is currently in preparation.

### 2020-01-15 paper_lap/manuscript.tex
updting paper

\usepackage{boxit}
%\newcommand{\boxit}[1]{#1}
%\newcommand{\dashboxit}[1]{#1}

@@

\section{Strong approximation of density away from corner panels}
\label{sec:appb}
In this section, we demonstrate that for a panel which is sufficiently far from the corner and  discretized using $M$ Gauss-Legendre nodes, the density computed using the adjoint of a Dirichlet discretization can be interpolated 
accurately at any point on the panel. As before let $\Omega$ denote a polygonal domain with boundary $\Gamma$. Let
$L$ denote the length of the boundary, and let $\gamma: [-L/2,L/2]\to \mathbb{R}^2$ denote an arc-length parameterization of the boundary.
Assume that the discretization satisfies the following assumptions:
\begin{enumerate}
\item All panels which are not at a corner, are separated from the closest corner by at least their panel length.
\item Let $E_{\rho}(\Gamma_{i})$ denote the Bernstein $\rho-$ellipse (see \cite{tref_approx}) corresponding to the panel $\Gamma_{i}$, and let $\rho_{i}$ 
be such that $E_{\rho_{i}}(\Gamma_{i})$ does not intersect $\Gamma \setminus S_{\Gamma_{i}}$, where 
$S_{\Gamma_{i}}$ is the edge containing $\Gamma_{i}$ (see~\cref{fig:illus-cons}). Let $\rho_{0} = \min_{i} \rho_{i} >1$.
\item All panels which are not adjacent to a panel at the corner, are separated from the corner by $2r_{c}$ where $r_{c}$ 
denotes the length of the panel at the corner.
\end{enumerate}
Under these assumptions, it can be shown that the accuracy of computing the
Legendre coefficients of the density (at panels which are not adjacent to a corner panel) for the Neumann problem using the adjoint discretization is related to the accuracy 
in the computation of the solution to an associated Dirichlet problem.
\begin{figure}
\begin{center}
\includegraphics[width=0.3\linewidth]{media/geom-restriction-illus}
\caption{Illustrative figure for demonstrating constraints required on the geometry discretization. The panel $\Gamma_{i}$ satisfies restriction 1 if $L_{i}/L_{0}>1$. Panel $\Gamma_{j}$ illustrates the largest Bernstein ellipse which intersects the other edges, and Panel $\Gamma_{k}$ illustrates restriction 3 if $r_{k}>2r_{c}$. }
\label{fig:illus-cons}
\end{center}
\end{figure}

@@

For any $s$ which is contained on the same segment as $\gamma_{[s_{1},s_{2}]}$, the kernel $k(s,t)$ is identically $0$.
Thus the boundary data $\tilde{f}(s)=0$  on the same edge as the panel $\gamma([s_{1},s_{2}])$. 
We further observe that $f(t)$ is an entire function when extended to the complex plane, since it is a Legendre polynomial.
Moreover, the nearest singularity of the function $k(s,t)$ in the complex plane as a function of $t$ is at $\gamma(s)$.
From assumption 2, it follows that
the error in computing $\tilde{f}(s)$ using an $M$ point Gauss-Legendre rule is bounded by $C \rho_{0}^{-M}$, where
the constant $C$ is related to the smoothness of $k(s,t)$ as a function of $t \in \mathbb{C}.$
Thus the function $\tilde{f}(s)$ can be computed to any desired precision by increasing the order of quadrature nodes
used to compute the integrals.

>>>>

%\usepackage{boxit}
%\newcommand{\boxit}[1]{#1}
%\newcommand{\dashboxit}[1]{#1}

@@

\section{Strong approximation of density away from corner panels}
\label{sec:appb}
In this section, we demonstrate that for a panel which is sufficiently far from the corner and  discretized using $M$ Gauss-Legendre nodes, the density computed using the adjoint of a Dirichlet discretization can be interpolated 
accurately at any point on the panel. As before let $\Omega$ denote a polygonal domain with boundary $\Gamma$. Let
$L$ denote the length of the boundary, and let $\gamma: [0,L]\to \mathbb{R}^2$ denote an arc-length parameterization of the boundary.
Assume that the discretization satisfies the following assumptions:
\begin{enumerate}
\item All panels which are not at a corner, are separated from the closest corner by at least their panel length.
\item Let $E_{\rho}(\Gamma_{i})$ denote the Bernstein $\rho-$ellipse (see \cite{tref_approx}) corresponding to the panel $\Gamma_{i}$, and let $\rho_{i}$ 
be such that $E_{\rho_{i}}(\Gamma_{i})$ does not intersect $\Gamma \setminus S_{\Gamma_{i}}$, where 
$S_{\Gamma_{i}}$ is the edge containing $\Gamma_{i}$ (see~\cref{fig:illus-cons}). Let $\rho_{0} = \min_{i} \rho_{i} >1$.
\item All panels which are not adjacent to a panel at the corner, are separated from the corner by $2r_{c}$ where $r_{c}$ 
denotes the length of the panel at the corner.
\end{enumerate}
Under these assumptions, it can be shown that the accuracy of computing the
Legendre coefficients of the density (at panels which are not adjacent to a corner panel) for the Neumann problem using the adjoint discretization is related to the accuracy 
in the computation of the solution to an associated Dirichlet problem.
\begin{figure}
\begin{center}
\includegraphics[width=0.3\linewidth]{paper-figs/geom-restriction-illus}
\caption{Illustrative figure for demonstrating constraints required on the geometry discretization. The panel $\Gamma_{i}$ satisfies restriction 1 if $L_{i}/L_{0}>1$. Panel $\Gamma_{j}$ illustrates the largest Bernstein ellipse which intersects the other edges, and Panel $\Gamma_{k}$ illustrates restriction 3 if $r_{k}>2r_{c}$. }
\label{fig:illus-cons}
\end{center}
\end{figure}

@@

For any $s$ which is contained on the same segment as $\gamma([s_{1},s_{2}])$, the kernel $k(s,t)$ is identically $0$.
Thus the boundary data $\tilde{f}(s)=0$  on the same edge as the panel $\gamma([s_{1},s_{2}])$. 
We further observe that $f(t)$ is an entire function when extended to the complex plane, since it is a Legendre polynomial.
Moreover, the nearest singularity of the function $k(s,t)$ in the complex plane as a function of $t$ is at $\gamma(s)$.
From assumption 2, it follows that
the error in computing $\tilde{f}(s)$ using an $M$ point Gauss-Legendre rule is bounded by $C \rho_{0}^{-M}$, where
the constant $C$ is related to the smoothness of $k(s,t)$ as a function of $t \in \mathbb{C}.$
Thus the function $\tilde{f}(s)$ can be computed to any desired precision by increasing the order of quadrature nodes
used to compute the integrals.
